\thetitle

### 2021-02-23 writing/mutate-interesting.tex
space war

To avoid these pitfalls, an \emph{interesting debugging scenario} is defined as
a mutation that satisfies three conditions.

First, {\em the mutation is rejected by the type checker when all missing type
annotations are restored\/}. This first criterion validates that the debugging
scenario concerns an actual type-level mistake.

@@

Third, {\em the exception's stack trace mentions at least three distinct
components\/}, meaning the scenario demands a sufficiently sophisticated
debugging effort: one due to the interaction between the buggy portion of the
program with the rest of the program.  In these cases, the rational programmer
may need to examine several modules of the program to locate the source of the
faulty interaction.  In technical terms, if the stack trace mentions at least
two distinct components, the bug should be revealed by the run-time checks
governing an interaction. A third component is required because all benchmark
programs come with a driver component, which is present in the stack trace of
all run-time errors. In essence, this last criterion excludes a large number of
trivial-to-debug scenarios that error immediately when their mutated component
is evaluated.

>>>>

To avoid these pitfalls, an \emph{interesting debugging scenario} is
defined as a mutation that satisfies three conditions.  First, {\em
the mutation is rejected by the type checker when all missing type
annotations are restored\/}. This first criterion validates that the
debugging scenario concerns an impedance mismatch.

@@

Third, {\em the exception's stack trace mentions at least three
distinct components\/}, meaning the scenario demands a sufficiently
sophisticated debugging effort: one due to the interaction between the
buggy portion of the program with the rest of the program.  In these
cases, the rational programmer must examine at least modules to locate
the source of the faulty interaction.  In technical terms, if the
stack trace mentions at least two distinct components, the bug should
be revealed by the run-time checks governing an interaction. A third
component is required because all benchmark programs include a driver
component, which is guaranteed to be in the stack trace. In essence,
this last criterion excludes a large number of trivial-to-debug
scenarios that error immediately when their mutated component is
evaluated.
